\chapter{Conclusion and Future Work}
\section{Conclusion}
In this work, we presented a novel \textbf{Dual-Path Event Detection and Classification} framework that effectively reconciles the trade-off between real-time responsiveness and semantic depth. By decoupling latency-sensitive clustering (Fast Path) from computationally intensive LLM reasoning (Slow Path), our system achieves near-instantaneous event detection on the Fast Path (2.4s processing latency under our test setup) while maintaining strong clustering quality on the labeled Mini-Ground Truth subset through News Anchoring (base SAHC: NMI = 0.54, Purity = 0.65; full hybrid pipeline: best NMI = 0.5978).
On the full dataset, intrinsic metrics and LLM-as-a-Judge evaluation further confirm improved cluster coherence over baseline methods. We demonstrated that traditional density-based methods alone are insufficient for noisy social data, requiring a hybrid approach where confirmed news serves as a semantic stabilizer. Future work will focus on deploying quantized embedding models to edge devices and integrating multi-modal signals (images/video) to further enhance situational awareness for crisis management.

\section{Future Work}
To scale the system toward production deployment ($>10{,}000$ events per second), we plan the following extensions:
\begin{itemize}
    \item \textbf{Model Optimization:} Apply quantization (ONNX/INT8) and batching-aware inference to reduce embedding latency and cost while preserving clustering quality.
    \item \textbf{Advanced Affect Modeling:} Extend the current 3-class sentiment to fine-grained emotions (e.g., Anger, Fear, Hope) to better characterize crisis dynamics and public reactions.
    \item \textbf{Human Feedback Loop:} Add dashboard-level correction tools (merge/split clusters, relabel taxonomy) and feed validated edits back into Active Learning for continual improvement.
    \item \textbf{Production Scaling:} Migrate from Spark Local to a distributed deployment on \textbf{Kubernetes/YARN}, enabling independent horizontal scaling of Kafka, Spark executors, and LLM workers.
\end{itemize}
