% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[utf8]{inputenc}
\usepackage[T1,T5]{fontenc}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds}
\usepackage[a4paper,left=30mm,right=30mm]{geometry}
%
\begin{document}
%
\title{Real-time Event Detection and Classification System: Integrating Social Streams and Mainstream News with LLM Intelligence}
\titlerunning{Real-time Event Detection and Classification System}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Nhat Tang\inst{1} \and
  Minh Nhut Le\inst{1} \and
  Do Trong Hop\inst{2} \and
  Nguyen Ngoc Quy\inst{2}}
%

% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science\\
  University of Information Technology, VNU-HCM\\
  \email{\{22521027, 22521060\}@gm.uit.edu.vn} \and
  Faculty of Information and Computer Engineering\\
  University of Information Technology, VNU-HCM\\
  \email{\{hopdt, quynn\}@uit.edu.vn}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  In the era of information overload, rapidly detecting and understanding emerging events from social streams is crucial for public safety and market intelligence.
  However, practical systems face two core challenges: (i) \textit{semantic ambiguity} in short, noisy social posts, and (ii) an \textit{evaluation gap} due to the lack of labels in streaming data.
  We present a \textbf{real-time event detection and classification system} built on a novel \textbf{Social-Aware Hierarchical Clustering (SAHC)} strategy and a \textbf{dual-path architecture} that combines Spark/Kafka for low-latency detection with asynchronous LLM workers for deep semantic refinement.
  On a \textbf{Mini-Ground Truth} subset (N=300 manually labeled social posts), our full hybrid pipeline achieves \textbf{NMI = 0.5978}.
  On the full dataset of 7{,}605 items, we report intrinsic clustering metrics (Silhouette, Davies--Bouldin, noise ratio) and an \textbf{LLM-as-a-Judge} protocol to assess semantic coherence at scale.

  \keywords{Event Detection and Classification \and Social Media Mining \and Real-time Streaming \and Large Language Models \and Hybrid Clustering.}
\end{abstract}

%
% Main Content - Chapters
%
\input{chapters/01_introduction}
\input{chapters/02_related_work}
\input{chapters/03_preliminaries}
\input{chapters/04_architecture}
\input{chapters/05_methodology}
\input{chapters/06_experiments}
\input{chapters/07_results}
\input{chapters/08_discussion}
\input{chapters/09_conclusion}
\input{chapters/10_ethics}

\begin{credits}
  \subsubsection{\ackname} We would like to express our sincere gratitude to Dr. Do Trong Hop and Mr. Nguyen Ngoc Quy for their invaluable supervision, critical insights, and continuous support throughout the development of this research. Their expert guidance on system architecture and methodology was instrumental in the success of this project.
\end{credits}

\bibliographystyle{splncs04}
\bibliography{refs}

\appendix
\input{chapters/11_appendix}

\end{document}
